The Third Bellman Equation

### 2019-01-29 paper/thirdbell.tex

>>>>

This computes the value functions of all rewards for a given policy.
Obviously when changing the policy, we may not change the policy in
several ways at once. For this we have to introduce targets (options) in
the policy.

\paragraph{All targets at once.} Let $\omega$ be an input to the policy,
which represents its current ``target''. We want to learn a policy with
input $\omega$, together with a function $\Omega$ that maps each state
$s$ to a target $\Omega(s)$, such that if we follow the policy with
target $\Omega(s)$, then we move towards $s$.

Concretely, we now have a function $z(s_1,s_2;\omega)$ which corresponds
to the inverse Laplacian of the MDP using policy $\omega$. It is learned
as above. Then we learn the parameters of $\pi(a|s,\omega)$ and of
$\Omega$ so as to maximize the time spent in $s$ when using policy
$\pi(\cdot|\Omega(s))$. Concretely, policy gradient is
\begin{equation}
\E_{s_1\sim \mu,\,a\sim \pi(a|s_1,\Omega(s)),\,s'\sim P(s'|s_1,a)}
\partial \ln \pi(a|s_1,\Omega(s))(\1_{s_1=s}+\gamma
z(s',s;\Omega(s))-z(s_1,s;\Omega(s)))
\end{equation}
(TODO: the $\1_{s_1=s}$ becomes a Dirac in the continuous case??)

I think the policy gradient above covers both the parameters of the
policy and the parameters of $\Omega$ (we can pretend the policy takes
$s$ as its target and that computing $\Omega$ is part of the policy).
But this conflicts with my previous intuition that we should train
$\Omega(s)$ to maximize $z(s',s;\Omega(s))$, which is the locally optimal
choice. I think we are missing some terms coming from the gradients of
$z(s_1,s;\Omega(s))$ when updating $\Omega$. TODO!! (Might be correct in
the end. Write that we want to maximize expected time spent in $s$ for
policy $\Omega(s)$. Write policy gradient for the policy with target $\Omega(s)$,
seeing $\Omega$ as part of the policy. Its policy gradient involves the
value function for policy $\Omega(s)$, which is given by $z(;\Omega(s))$,
but it does not involves the gradients of the value function.)

Problem here: $\mu$ has to be the invariant distribution of the
$\Omega(s)$-policy, so a bit complicated to apply online, we need to keep
the policy fixed until convergence... this implies having separate runs
with different targets. Or find an off-policy version...

$\omega$ represents an option, but there is no risk of option collapse
because each option has a different target.

This still does not cover policies with arbitrary rewards $R$. We have to
find a representation $\Omega(R)$. We could try to enforce linearity of
$\Omega$, namely, train things such that the policy with parameter
$\omega=\E_{s\sim \rho} \Omega(s)R(s)$ maximizes $R$, for every $R$ in some
class. If the class includes Dirac, then 
the policy with parameter
$\Omega(s)$ indeed maximizes time spend in $s$. (This might help with the
Dirac in the policy gradient above.)
